Designing Turk Experiments for Visual Statistical Inference

### 2013-06-20 paper_turk.tex
creating task

\item {\bf Duration of the experiment:} The duration of each experiment is a period of time set so that the task is not available after that time period no matter whether all the required number of workers have participated or not.

\item {\bf Redirect to new web:} The MTurk worker should be informed clearly that they will be redirect to a new website from where they will provide feedback. The whole task including the instruction and procedure in the web application presented as per the task plan described in Section \ref{sec:task_plan}.

>>>>

\item Duration of the task is the period of time the task is available for workers to do. If the time period is over the task will not be available no matter whether all the required number of workers have participated or not. This duration is important as each payment has to be finalized by this time period. Otherwise, all the workers will be paid automatically after this time period no matter if the the task is accepted or rejected. Some times it is helpful to set up a longer duration and see how long it takes before all the tasks get completed.

\item Finally, the workers are redirected to the web site designed for lineup evaluation. MTurk workers should be informed clearly that they will be redirected to a new website from where they will provide feedback. The whole task including the instructions and procedures in the web application should be presented as per the task plan described in Section \ref{sec:task_plan}.
